%-------------------------
% Rover Resume - Base Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[9pt]{article} % fontsize 9pt

\usepackage[margin=0.5in, a4paper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
\titlespacing{\section}{0pt}{4pt}{4pt}
\titlespacing{\subsection}{0pt}{2pt}{1pt}
\titlespacing{\subsubsection}{0pt}{0pt}{2pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,leftmargin=*}
\pagestyle{empty} % remove page number
\pdfgentounicode=1
\usepackage[bookmarks=false]{hyperref}
\usepackage{xcolor}

\begin{document}

\begin{center}
    \begin{minipage}{0.45\textwidth}
        {\Huge\bfseries
            Harik Sodhi % Name Here
        } \\ \medskip
    \end{minipage} \hfill
    \begin{minipage}{0.5\textwidth}
        \raggedleft
        Email: harik.sodhi@chch.ox.ac.uk \\
        Mobile: +44 (0) 7799 171770 \\
        LinkedIn: \href{https://linkedin.com/in/harik-sodhi}{linkedin.com/in/harik-sodhi}\\
        GitHub: \href{https://github.com/harik-s}{github.com/harik-s}\\
    \end{minipage}
\end{center}

\section{Education}

\subsection{University of Oxford (Christ Church) $|$ {\normalfont\itshape MEng Engineering Science} \hfill Oct 2025 -- Jun 2029}
\begin{itemize}
    \item Relevant modules: Engineering Mathematics, Structures and Mechanics, Electrical and Information Engineering, Energy.
\end{itemize}

\section{Awards \& Honours}

\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item Silver Medal, International Physics Olympiad (49th/420 competitors from 89 countries; highest-ranked competitor from Western Europe) \hfill 2025
    \item United Kingdom International Physics Olympiad Team Member \hfill 2025
    \item Purple Comet Mathematics Competition --- UK National Champion \hfill 2024
    \item Winner, Berkeley Math Tournament Online Power Round \hfill 2024
    \item British Mathematical Olympiad Round 1 Distinction \hfill 2024
    \item Ritange Winner out of 1200 teams (Team Captain) \hfill 2023
\end{itemize}

\section{Experience}

\subsection{Oxford Alpha Fund \hfill Oxford}
\subsubsection{Quant Analyst / Director \hfill Jan 2026 -- Present}
\begin{itemize}
    \item Selected through a competitive quantitative research and presentation process as a first-year undergraduate.
    \item Researched volatility risk premia in short-dated Bitcoin options using historical Deribit/Coinbase data; developed and backtested systematic trading strategies achieving a Sharpe ratio of 1.18 and a 70\% win rate. {\small\href{https://github.com/Harik-S/oaf-hilary-2026}{\textbf{[Code]}}}
    \item Built automated tooling to generate sponsor-ready CV books from member CVs, streamlining recruitment preparation.
    \item Coordinated with sponsoring firms and industry partners to support recruitment events and strengthen fund relationships.
\end{itemize}

\subsection{Optiver Trading Academy \hfill Oxford}
\subsubsection{Participant \hfill Oct 2025 -- Nov 2025}
\begin{itemize}
    \item Selected for Optiver's competitive Trading Academy programme as a first-year undergraduate.
    \item Traded ETFs and futures on Optiver's proprietary simulation platform, applying market-making, delta-hedging, and risk-management principles under realistic market conditions.
\end{itemize}

\section{Leadership \& Activities}

\subsection{VEX Robotics \& REC Foundation \hfill London / Remote}
\subsubsection{Global Student Advisory Board Member \& Team Captain \hfill May 2021 -- Mar 2024}
\begin{itemize}
    \item Selected as one of 12 members globally to directly advise the CEO and executive leadership team on the strategic direction and accessibility of the VEX Robotics programme.
    \item Served as Team Captain, Lead Programmer, and Lead Designer; managed team operations and spearheaded end-to-end development of competitive robots.
    \item Engineered autonomous routines and driver-assist features in C++ (PROS), implementing closed-loop control systems (PID) for precise chassis positioning and kinematic sub-systems.
    \item Utilized 3D CAD software to design structurally optimized mechanisms, translating game constraints into high-performance hardware.
\end{itemize}

\section{Projects}

\subsection{Market Making Simulator}
\begin{itemize}
    \item Developed a multi-agent market simulation modelling market makers, noise traders, and informed traders.
    \item Analysed the effects of participant composition on spread formation, adverse selection, and trading profitability.
    \item Implemented strategy evaluation and performance analysis tools for comparing trading behaviour. {\small\href{https://github.com/Harik-S/oafbc-project/tree/game-implementation}{\textbf{[GitHub]}}}
\end{itemize}

\subsection{Rocket Lander}
\begin{itemize}
    \item Designed and developed a MATLAB simulation of autonomous rocket landing dynamics from first principles, incorporating variable-mass propulsion, atmospheric drag, and gravity.
    \item Implemented Runge-Kutta numerical integration, a scratch-built PID control system, and constrained optimisation techniques to achieve stable autonomous touchdowns. {\small\href{https://github.com/Harik-S/touch-down}{\textbf{[GitHub]}}}
\end{itemize}

\section{Skills}
\begin{itemize}[leftmargin=*, itemsep=0pt]
    \item \textbf{Programming Languages:} Python, MATLAB, LaTeX, C++
    \item \textbf{Libraries \& Frameworks:} NumPy, Pandas, Matplotlib, Tkinter, PyTorch, Scikit-learn, PyPDF2, IPython
    \item \textbf{Developer Tools:} Git, GitHub
\end{itemize}

\end{document}