%-------------------------
% Rover Resume - Base Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[9pt]{article} % fontsize 9pt

\usepackage[margin=0.5in, a4paper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
\titlespacing{\section}{0pt}{4pt}{4pt}
\titlespacing{\subsection}{0pt}{2pt}{1pt}
\titlespacing{\subsubsection}{0pt}{0pt}{2pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,leftmargin=*}
\pagestyle{empty} % remove page number
\pdfgentounicode=1
\usepackage[bookmarks=false]{hyperref}
\usepackage{xcolor}

\begin{document}

\begin{center}
    \begin{minipage}{0.45\textwidth}
        {\Huge\bfseries
            Harik Sodhi % Name Here
        } \\ \medskip
    \end{minipage} \hfill
    \begin{minipage}{0.5\textwidth}
        \raggedleft
        Email: harik.sodhi@chch.ox.ac.uk \\
        Mobile: +44 (0) 7799 171770 \\
        LinkedIn: \href{https://linkedin.com/in/harik-sodhi}{linkedin.com/in/harik-sodhi}\\
        GitHub: \href{https://github.com/harik-s}{github.com/harik-s}\\
    \end{minipage}
\end{center}
\section{Awards \& Honours}

\begin{itemize}[leftmargin=*]
    \item \textbf{Silver Medal, International Physics Olympiad} (2025) -- 49th/420 competitors from 89 countries; highest-ranked competitor from Western Europe.
    
    \item \textbf{United Kingdom International Physics Olympiad Team Member} (2025) -- Selected after Gold awards in BPhO Round 2 and BAAO Round 2.
    
    \item \textbf{Winner, Berkeley Math Tournament Online Power Round} (2024) -- First place in a proof-based competition on graph theory, cryptography, and computational complexity.
    
	\item \textbf{Ritangle National Champion} (2023) -- Team Captain; 1st/1,200 teams in a national combinatorial optimisation challenge, developing and proving an optimal solution to a highly constrained scheduling problem with hundreds of interacting variables.
\end{itemize}

\section{Education}

\subsection{University of Oxford (Christ Church) $|$ {\normalfont\itshape MEng Engineering Science} \hfill Oct 2025 -- Jun 2029}
\begin{itemize}
    \item First-year: 93\% labs, 92\% internal exams
\end{itemize}


\section{Experience}

\subsection{Oxford Alpha Fund \hfill Oxford}
\subsubsection{Quant Analyst / Director \hfill Jan 2026 -- Present}
\begin{itemize}
    \item Selected through a competitive quantitative research and presentation process as a first-year undergraduate.
    \item Researched volatility risk premia in short-dated Bitcoin options using historical Deribit/Coinbase data; developed and backtested systematic trading strategies achieving a Sharpe ratio of 1.18 and a 70\% win rate. {\small\href{https://github.com/Harik-S/oaf-hilary-2026}{\textbf{[Code]}}}
    \item Serve on the general committee, contributing to the Walton Edge newsletter, sponsor liaison, and candidate evaluation.
\end{itemize}

\subsection{Optiver Trading Academy \hfill Oxford}
\subsubsection{Participant \hfill Oct 2025 -- Nov 2025}
\begin{itemize}
    \item Selected for Optiver's competitive Trading Academy programme as a first-year undergraduate.
    \item Traded ETFs and futures on Optiver's proprietary simulation platform, applying market-making, delta-hedging, and risk-management principles under realistic market conditions.
\end{itemize}

\section{Leadership \& Activities}

\subsection{VEX Robotics \& REC Foundation \hfill London / Remote}
\subsubsection{Global Student Advisory Board Member \& Team Captain \hfill May 2021 -- Mar 2024}
\begin{itemize}
    \item Selected as one of 12 members globally to directly advise the CEO and executive leadership team on the strategic direction, international expansion, and accessibility of the REC Foundation—the governing body of the world’s largest robotics competition spanning 2,400+ teams from 60+ countries and major corporate partnerships (e.g., NASA).
    \item Served as Team Captain, Lead Programmer, and Lead Designer; managed team operations and spearheaded end-to-end development of competitive robots.
    \item Developed autonomous routines and driver-assist systems in C++ using PID control and designed competition mechanisms in CAD.
\end{itemize}

\section{Projects}

\subsection{Market Making Simulator \hfill Nov 2025}
\begin{itemize}
    \item Developed a multi-agent market simulation modelling market makers, noise traders, and informed traders.
    \item Analysed the effects of participant composition on spread formation, adverse selection, and trading profitability.
    \item Implemented strategy evaluation and performance analysis tools for comparing trading behaviour. {\small\href{https://github.com/Harik-S/oafbc-project/tree/game-implementation}{\textbf{[GitHub]}}}
\end{itemize}

\subsection{Rocket Lander \hfill Apr 2026}
\begin{itemize}
    \item Designed and developed a MATLAB simulation of autonomous rocket landing dynamics from first principles, incorporating variable-mass propulsion, atmospheric drag, and gravity.
    \item Implemented Runge-Kutta numerical integration, a scratch-built PID control system, and constrained optimisation techniques to achieve stable autonomous touchdowns. {\small\href{https://github.com/Harik-S/touch-down}{\textbf{[GitHub]}}}
\end{itemize}

\section{Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Programming:} Python, C++, MATLAB, LaTeX
    \item \textbf{Quantitative:} Statistical Modelling, Backtesting, Optimisation, Stochastic Simulation, Volatility Analysis, Numerical Methods
    \item \textbf{Libraries:} NumPy, Pandas, SciPy, PyTorch, Scikit-learn, Matplotlib
    \item \textbf{Tools:} Linux, Git, GitHub, SolidWorks
\end{itemize}

\end{document}